---
title: "15.TSA_codeAss"
output: 
  pdf_document: 
    keep_tex: yes
date: '2022-06-22'
---

# I. Preparation of data

## 1. Load packages and Initialize
```{r "1.1. Load packages and Initialize"}
# Load packages
library(openxlsx)
library(xts)
library(Matrix)
library(ggplot2)
library(forecast)
library(keras)
library(vars)
# Change default theme
theme_set(theme_bw(10))
# RMSE function
RMSE.val <- function(X.true, X.test){
return( sqrt( mean( (X.true - X.test)^2 ) ) )
}
```

## 2. Load and split data
```{r "1.2. Load and split data"}
# Load data
Elec = read.xlsx('Elec-train.xlsx', 1)
# Convert data to 'xts' object
colnames(Elec) = c('Timestamp', 'Power', 'Temp')
xts_Elec = xts(Elec[, c('Power', 'Temp')], order.by = strptime(Elec[, "Timestamp"], 
                                                               format = "%m/%d/%Y %H:%M"))
# Split data
xts_Elec.train = xts_Elec['/2010-02-15']
xts_Elec.test = xts_Elec['2010-02-16']
```

## 3. Plot data
```{r "1.3. Plot data"}
# Plot all data
autoplot(xts_Elec[, c('Power', 'Temp')], facets = NULL) + labs(x = "Days") +
  theme(legend.position="bottom")
```

```{r "1.3. plot of the first week"}
# plot of the first week
autoplot(xts_Elec['2010-01-01/2010-01-07', c('Power', 'Temp')], facets = NULL,
         main = "Plot of the first week") + 
  theme(legend.position="bottom")
```

```{r "1.3. Seasonal plot"}
# Create time series
ts_Elec.train = ts(coredata(xts_Elec.train), frequency = 96, start = c(1,6))
ts_Elec.test = ts(coredata(xts_Elec.test), frequency = 96, start = c(47,1))
# Seasonal plot
ggseasonplot(ts_Elec.train[, 'Power'])
```

```{r "Decompose of additive time series"}
# Decompose of additive time series
components_power = decompose(ts_Elec.train[, 'Power']) 
autoplot(components_power)
```

#---------------------------------------------------------------------------------------------#
# II. Forecast without using outdoor temperature

## 1. Split data into 4 parts
```{r "2.1. Split data into 4 parts"}
lxts_Elec.train = list(); lxts_Elec.test = list()
lts_Elec.train = list(); time.Elec.test = list()
for (i in 1:4){
  # Create a list of xts object.
  lxts_Elec.train[[i]] = xts_Elec.train[.indexmin(xts_Elec.train) == 15*(i-1)]
  lxts_Elec.test[[i]] = xts_Elec.test[.indexmin(xts_Elec.test) == 15*(i-1)]
  # Create list of time series object
  if (i == 1)
    lts_Elec.train[[i]] = ts(coredata(lxts_Elec.train[[i]]), frequency = 24, start = c(1,3))
  else
    lts_Elec.train[[i]] = ts(coredata(lxts_Elec.train[[i]]), frequency = 24, start = c(1,2))
  # Prepare time of each forecasted data part to create the xts object
  time.Elec.test[[i]] = time(lxts_Elec.test[[i]])
}
# Verification of data
for (i in 1:4){
  cat ('* --- Data', i, '(Minute', 15*(i-1), 'of each hour) --- *\n')
  print(tail(lxts_Elec.train[[i]], 3))
  print(tail(lts_Elec.train[[i]], 3))
}
```

## 2. Additive seasonal HoltWinters
```{r "2.2. Additive seasonal HoltWinters"}
fit4.hw1.add1 = list(); prev4.hw1.add1 = list(); lxts_prev4.hw1.add1 = list()
# Forecast and convert the results to xts objects.
for (i in 1:4){
  # Additive seasonal HoltWinters
  fit4.hw1.add1[[i]] = HoltWinters(lts_Elec.train[[i]][, 'Power'])
  prev4.hw1.add1[[i]] = forecast(fit4.hw1.add1[[i]], h = 24)
  lxts_prev4.hw1.add1[[i]] = xts(prev4.hw1.add1[[i]]$mean, order.by = time.Elec.test[[i]])
}
# Concatenate the 4 parts of forecasted data
xts_prev4.hw1.add1 = do.call(rbind, lxts_prev4.hw1.add1)
# Compute the RMSE
rmse4.hw1.add1 = RMSE.val(xts_prev4.hw1.add1, xts_Elec.test[, 'Power'])
cat ('RMSE of Additive seasonal HoltWinters =', rmse4.hw1.add1, '\n')
```
- RMSE of Additive seasonal HoltWinters = 15.22545 
---

## 3. Multiplicative seasonal HoltWinters
```{r "2.3. Multiplicative seasonal HoltWinters"}
fit4.hw1.mult1 = list(); prev4.hw1.mult1 = list(); lxts_prev4.hw1.mult1 = list()
# Forecast and convert the results to xts objects.
for (i in 1:4){
  # Multiplicative seasonal HoltWinters
  fit4.hw1.mult1[[i]] = HoltWinters(lts_Elec.train[[i]][, 'Power'], seasonal = "multiplicative")
  prev4.hw1.mult1[[i]] = forecast(fit4.hw1.mult1[[i]], h = 24)
  lxts_prev4.hw1.mult1[[i]] = xts(prev4.hw1.mult1[[i]]$mean, order.by = time.Elec.test[[i]])
}
# Concatenate the 4 parts of forecasted data
xts_prev4.hw1.mult1 = do.call(rbind, lxts_prev4.hw1.mult1)
# Compute the RMSE
rmse4.hw1.mult1 = RMSE.val(xts_prev4.hw1.mult1, xts_Elec.test[, 'Power'])
cat ('RMSE of Multiplicative seasonal HoltWinters =', rmse4.hw1.mult1, '\n')
```
- RMSE of Multiplicative seasonal HoltWinters = 16.67767 
---

## 4. Additive seasonal HW
```{r "2.4. Additive seasonal HW"}
fit4.hw2.add1 = list(); lxts_fit4.hw2.add1 = list()
fit4.hw2.add2 = list(); lxts_fit4.hw2.add2 = list()
fit4.hw2.add3 = list(); lxts_fit4.hw2.add3 = list()
fit4.hw2.add4 = list(); lxts_fit4.hw2.add4 = list()
# Forecast and convert the result to xts object
for (i in 1:4){
  # Additive seasonal HW
  fit4.hw2.add1[[i]] = hw(lts_Elec.train[[i]][,'Power'], h = 24)
  lxts_fit4.hw2.add1[[i]] = xts(fit4.hw2.add1[[i]]$mean, order.by = time.Elec.test[[i]])
  # Additive seasonal HW + damping
  fit4.hw2.add2[[i]] = hw(lts_Elec.train[[i]][,'Power'], h = 24, damped = T)
  lxts_fit4.hw2.add2[[i]] = xts(fit4.hw2.add2[[i]]$mean, order.by = time.Elec.test[[i]])
  # Additive seasonal HW + Box-Cox
  fit4.hw2.add3[[i]] = hw(lts_Elec.train[[i]][,'Power'], h = 24, lambda = 'auto')
  lxts_fit4.hw2.add3[[i]] = xts(fit4.hw2.add3[[i]]$mean, order.by = time.Elec.test[[i]])
  # Additive seasonal HW + damping + Box-Cox
  fit4.hw2.add4[[i]] = hw(lts_Elec.train[[i]][,'Power'], h = 24, damped = T, lambda = 'auto')
  lxts_fit4.hw2.add4[[i]] = xts(fit4.hw2.add4[[i]]$mean, order.by = time.Elec.test[[i]])
}
# Concatenate the 4 parts of forecasted data
xts_fit4.hw2.add1 = do.call(rbind, lxts_fit4.hw2.add1)
xts_fit4.hw2.add2 = do.call(rbind, lxts_fit4.hw2.add2)
xts_fit4.hw2.add3 = do.call(rbind, lxts_fit4.hw2.add3)
xts_fit4.hw2.add4 = do.call(rbind, lxts_fit4.hw2.add4)
# Compute the RMSE
rmse4.hw2.add1 = RMSE.val(xts_fit4.hw2.add1, xts_Elec.test[, 'Power'])
rmse4.hw2.add2 = RMSE.val(xts_fit4.hw2.add2, xts_Elec.test[, 'Power'])
rmse4.hw2.add3 = RMSE.val(xts_fit4.hw2.add3, xts_Elec.test[, 'Power'])
rmse4.hw2.add4 = RMSE.val(xts_fit4.hw2.add4, xts_Elec.test[, 'Power'])
# Print the RMSE
cat ('RMSE of Additive seasonal HW =', rmse4.hw2.add1, '\n')
cat ('RMSE of Additive seasonal HW with damping =', rmse4.hw2.add2, '\n')
cat ('RMSE of Additive seasonal HW with Box-Cox =', rmse4.hw2.add3, '\n')
cat ('RMSE of Additive seasonal HW with damping and Box-Cox =', rmse4.hw2.add4, '\n')
```
- RMSE of Additive seasonal HW = 15.75758 
---
- RMSE of Additive seasonal HW with damping = 15.37618 
---
- RMSE of Additive seasonal HW with Box-Cox = 15.898 
---
- RMSE of Additive seasonal HW with damping and Box-Cox = 16.12223 
---

## 5. Multiplicative seasonal HW
```{r "2.5. Multiplicative seasonal HW"}
fit4.hw2.mult1 = list(); lxts_fit4.hw2.mult1 = list()
fit4.hw2.mult2 = list(); lxts_fit4.hw2.mult2 = list()
# Forecast and convert the result to xts object
for (i in 1:4){
  # Multiplicative seasonal HW
  fit4.hw2.mult1[[i]] = hw(lts_Elec.train[[i]][, 'Power'], h = 24, seasonal = "multiplicative")
  lxts_fit4.hw2.mult1[[i]] = xts(fit4.hw2.mult1[[i]]$mean, order.by = time.Elec.test[[i]])
  # Multiplicative seasonal HW + damping
  fit4.hw2.mult2[[i]] = hw(lts_Elec.train[[i]][, 'Power'], h = 24, seasonal = "multiplicative",
                           damped = T)
  lxts_fit4.hw2.mult2[[i]] = xts(fit4.hw2.mult2[[i]]$mean, order.by = time.Elec.test[[i]])
}
# Concatenate the 4 parts of forecasted data
xts_fit4.hw2.mult1 = do.call(rbind, lxts_fit4.hw2.mult1)
xts_fit4.hw2.mult2 = do.call(rbind, lxts_fit4.hw2.mult2)
# Compute the RMSE
rmse4.hw2.mult1 = RMSE.val(xts_fit4.hw2.mult1, xts_Elec.test[, 'Power'])
rmse4.hw2.mult2 = RMSE.val(xts_fit4.hw2.mult2, xts_Elec.test[, 'Power'])
# Print the RMSE
cat ('RMSE of Multiplicative seasonal HW =', rmse4.hw2.mult1, '\n')
cat ('RMSE of Multiplicative seasonal HW with damping =', rmse4.hw2.mult2, '\n')
```
- RMSE of Multiplicative seasonal HW = 16.88001 
---
- RMSE of Multiplicative seasonal HW with damping = 16.84145 
---

## 6. Auto ARIMA
```{r "2.6. Auto ARIMA"}
fit4.autoArima1 = list(); prev4.autoArima1 = list(); lxts_prev4.autoArima1 = list()
fit4.autoArima2 = list(); prev4.autoArima2 = list(); lxts_prev4.autoArima2 = list()
# Forecast and convert the results to xts objects.
for (i in 1:4){
# Auto ARIMA
  fit4.autoArima1[[i]] = auto.arima(lts_Elec.train[[i]][, 'Power'])
  prev4.autoArima1[[i]] = forecast(fit4.autoArima1[[i]], h = 24)
  lxts_prev4.autoArima1[[i]] = xts(prev4.autoArima1[[i]]$mean, order.by = time.Elec.test[[i]])
  # Auto ARIMA + Box-Cox
  fit4.autoArima2[[i]] = auto.arima(lts_Elec.train[[i]][, 'Power'], lambda = 'auto')
  prev4.autoArima2[[i]] = forecast(fit4.autoArima2[[i]], h = 24)
  lxts_prev4.autoArima2[[i]] = xts(prev4.autoArima2[[i]]$mean, order.by = time.Elec.test[[i]])
}
# Concatenate the 4 parts of forecasted data
xts_prev4.autoArima1 = do.call(rbind, lxts_prev4.autoArima1)
xts_prev4.autoArima2 = do.call(rbind, lxts_prev4.autoArima2)
# Compute the RMSE
rmse4.autoArima1 = RMSE.val(xts_prev4.autoArima1, xts_Elec.test[, 'Power'])
rmse4.autoArima2 = RMSE.val(xts_prev4.autoArima2, xts_Elec.test[, 'Power'])
# Print the RMSE
cat ('RMSE of Auto ARIMA =', rmse4.autoArima1, '\n')
cat ('RMSE of Auto ARIMA with Box-Cox =', rmse4.autoArima2, '\n')
```
- RMSE of Auto ARIMA = 17.6711 
---
- RMSE of Auto ARIMA with Box-Cox = 17.08156 
---

## 7. NNET
```{r "2.7. NNET"}
fit4.nnet1 = list(); prev4.nnet1 = list(); lxts_prev4.nnet1 = list()
fit4.nnet2 = list(); prev4.nnet2 = list(); lxts_prev4.nnet2 = list()
# Forecast and convert the results to xts objects.
for (i in 1:4){
  # NNET
  fit4.nnet1[[i]] = nnetar(lts_Elec.train[[i]][, 'Power'])
  prev4.nnet1[[i]] = forecast(fit4.nnet1[[i]], h = 24)
  lxts_prev4.nnet1[[i]] = xts(prev4.nnet1[[i]]$mean, order.by = time.Elec.test[[i]])
  # NNET + Box-Cox
  fit4.nnet2[[i]] = nnetar(lts_Elec.train[[i]][, 'Power'], lambda = 'auto')
  prev4.nnet2[[i]] = forecast(fit4.nnet2[[i]], h = 24)
  lxts_prev4.nnet2[[i]] = xts(prev4.nnet2[[i]]$mean, order.by = time.Elec.test[[i]])
}
# Concatenate the 4 parts of forecasted data
xts_prev4.nnet1 = do.call(rbind, lxts_prev4.nnet1)
xts_prev4.nnet2 = do.call(rbind, lxts_prev4.nnet2)
# Compute the RMSE
rmse4.nnet1 = RMSE.val(xts_prev4.nnet1, xts_Elec.test[, 'Power'])
rmse4.nnet2 = RMSE.val(xts_prev4.nnet2, xts_Elec.test[, 'Power'])
# Print the RMSE
cat ('RMSE of NNET =', rmse4.nnet1, '\n')
cat ('RMSE of NNET with Box-Cox =', rmse4.nnet2, '\n')
```
- RMSE of NNET = 15.25623 
---
- RMSE of NNET with Box-Cox = 15.85518
---

## 8. SARIMA

### Plot
```{r "2.8.a. Plot"}
for (i in 1:4){
  titleOfPlot = paste('Data ', i, ' (Minute ', 15*(i-1), ' of each hour)' , sep='')
  ggtsdisplay(lts_Elec.train[[i]][, 'Power'], main = titleOfPlot)
}
```

### Differencing : lag=24
```{r "2.8.b. Differencing : lag=24"}
power.diff0 = list()
for (i in 1:4){
  titleOfPlot = paste('diff(lag=24) of data ', i, ' (Minute ', 15*(i-1), ' of each hour)' , sep='')
  power.diff0[[i]] = diff(lts_Elec.train[[i]][, 'Power'], lag = 24)
  ggtsdisplay(power.diff0[[i]], main = titleOfPlot)
}
```

### Differencing : lag(lag=24)
```{r "2.8.c. Differencing : lag(lag=24)"}
power.diff1 = list()
for (i in 1:4){
  titleOfPlot = paste('diff(diff(lag=24)) of data ', i, ' (Minute ', 15*(i-1), ' of each hour)' ,
                      sep='')
  power.diff1[[i]] = diff(power.diff0[[i]])
  ggtsdisplay(power.diff1[[i]], main = titleOfPlot)
}
```

### SARIMA(0,1,3)(0,1,1)[24]
```{r "2.8.d. SARIMA(0,1,3)(0,1,1)24"}
fit4.arima11 = list()
# Create the model
for (i in 1:4){
  # SARIMA(0,1,3)(0,1,1)[24]
  fit4.arima11[[i]] = Arima(lts_Elec.train[[i]][, 'Power'], order = c(0,1,3), seasonal = c(0,1,1))
  # Check residuals
  cat ('* --- Data', i, '(Minute', 15*(i-1), 'of each hour) --- *\n')
  checkresiduals(fit4.arima11[[i]])
}
```
* --- Data 1 (Minute 0 of each hour) --- *

	Ljung-Box test

data:  Residuals from ARIMA(0,1,3)(0,1,1)[24]
Q* = 57.263, df = 44, p-value = 0.0866

Model df: 4.   Total lags used: 48

* --- Data 2 (Minute 15 of each hour) --- *

	Ljung-Box test

data:  Residuals from ARIMA(0,1,3)(0,1,1)[24]
Q* = 47.588, df = 44, p-value = 0.3288

Model df: 4.   Total lags used: 48

* --- Data 3 (Minute 30 of each hour) --- *

	Ljung-Box test

data:  Residuals from ARIMA(0,1,3)(0,1,1)[24]
Q* = 61.639, df = 44, p-value = 0.04056

Model df: 4.   Total lags used: 48

* --- Data 4 (Minute 45 of each hour) --- *

	Ljung-Box test

data:  Residuals from ARIMA(0,1,3)(0,1,1)[24]
Q* = 57.703, df = 44, p-value = 0.08056

Model df: 4.   Total lags used: 48

### SARIMA(0,1,7)(0,1,1)[24]
```{r "2.8.e. SARIMA(0,1,7)(0,1,1)24"}
fit4.arima21 = list(); fit4.arima22 = list();
# Create the model
for (i in 1:4){
  # SARIMA(0,1,7)(0,1,1)[24]
  fit4.arima21[[i]] = Arima(lts_Elec.train[[i]][, 'Power'], order = c(0,1,7), seasonal = c(0,1,1))
  # SARIMA(0,1,7)(0,1,1)[24] + Box-Cox
  fit4.arima22[[i]] = Arima(lts_Elec.train[[i]][, 'Power'], order = c(0,1,7), seasonal = c(0,1,1),
  lambda = 'auto')
  # Check residuals of SARIMA(0,1,7)(0,1,1)[24]
  cat ('* --- Data', i, '(Minute', 15*(i-1), 'of each hour) --- *\n')
  checkresiduals(fit4.arima21[[i]], plot = F)
}
```
* --- Data 1 (Minute 0 of each hour) --- *

	Ljung-Box test

data:  Residuals from ARIMA(0,1,7)(0,1,1)[24]
Q* = 48.524, df = 40, p-value = 0.167

Model df: 8.   Total lags used: 48

* --- Data 2 (Minute 15 of each hour) --- *

	Ljung-Box test

data:  Residuals from ARIMA(0,1,7)(0,1,1)[24]
Q* = 43.77, df = 40, p-value = 0.3145

Model df: 8.   Total lags used: 48

* --- Data 3 (Minute 30 of each hour) --- *

	Ljung-Box test

data:  Residuals from ARIMA(0,1,7)(0,1,1)[24]
Q* = 44.469, df = 40, p-value = 0.2891

Model df: 8.   Total lags used: 48

* --- Data 4 (Minute 45 of each hour) --- *

	Ljung-Box test

data:  Residuals from ARIMA(0,1,7)(0,1,1)[24]
Q* = 41.299, df = 40, p-value = 0.4137

Model df: 8.   Total lags used: 48

```{r "2.8.f. Forecast SARIMA"}
prev4.arima21 = list(); lxts_prev4.arima21 = list()
prev4.arima22 = list(); lxts_prev4.arima22 = list()
# Forecast and convert the results to xts objects.
for (i in 1:4){
  # SARIMA(0,1,7)(0,1,1)[24]
  prev4.arima21[[i]] = forecast(fit4.arima21[[i]], h = 24)
  lxts_prev4.arima21[[i]] = xts(prev4.arima21[[i]]$mean, order.by = time.Elec.test[[i]])
  # SARIMA(0,1,7)(0,1,1)[24] + Box-Cox
  prev4.arima22[[i]] = forecast(fit4.arima22[[i]], h = 24)
  lxts_prev4.arima22[[i]] = xts(prev4.arima22[[i]]$mean, order.by = time.Elec.test[[i]])
  }
  # Concatenate the 4 parts of forecasted data
  xts_prev4.arima21 = do.call(rbind, lxts_prev4.arima21)
  xts_prev4.arima22 = do.call(rbind, lxts_prev4.arima22)
# Compute the RMSE
rmse4.arima21 = RMSE.val(xts_prev4.arima21, xts_Elec.test[, 'Power'])
rmse4.arima22 = RMSE.val(xts_prev4.arima22, xts_Elec.test[, 'Power'])
# Print the RMSE
cat ('RMSE of SARIMA(0,1,7)(0,1,1)[24] =', rmse4.arima21, '\n')
cat ('RMSE of SARIMA(0,1,7)(0,1,1)[24] with Box-Cox =', rmse4.arima22, '\n')
```
- RMSE of SARIMA(0,1,7)(0,1,1)[24] = 14.68489 
---
- RMSE of SARIMA(0,1,7)(0,1,1)[24] with Box-Cox = 14.70515 
---

## 9. Choose the model

### Model summary
```{r "2.9.a. Model summary"}
df = data.frame(RMSE = c(rmse4.hw1.add1, rmse4.hw1.mult1, rmse4.hw2.add2, rmse4.hw2.mult2,
                         rmse4.autoArima2, rmse4.nnet1, rmse4.arima21))
rownames(df) = c("Additive seasonal HoltWinters", "Multiplicative seasonal HoltWinters",
                 "Additive seasonal HW + damping","Multiplicative seasonal HW + damping",
                 "Auto ARIMA + Box-Cox", "NNET", "SARIMA(0,1,7)(0,1,1)[24]")
print(df)
```
                                          RMSE
                                         <dbl>
Additive seasonal HoltWinters	        15.22545			
Multiplicative seasonal HoltWinters	  16.67767			
Additive seasonal HW + damping	      15.37618			
Multiplicative seasonal HW + damping	16.84145			
Auto ARIMA + Box-Cox                	17.08156			
NNET	                                15.25623			
SARIMA(0,1,7)(0,1,1)[24]            	14.68489

### Plot
```{r "2.9.b Plot"}
xts_prevAndTest = cbind(xts_prev4.arima21, xts_Elec.test[, 'Power'])
names(xts_prevAndTest) = c("SARIMA(0,1,7)(0,1,1)[24]", "True data")
autoplot(xts_prevAndTest, facets = NULL) + labs(x = 'Days', y = 'Power (kW)') +
  theme(legend.position="bottom")
```

## 10. Forecast using all data

### Prepare data
```{r "2.10.a Prepare data"}
# Initialization
xts_Elec.fit = xts_Elec['/2010-02-16']
xts_Elec.prev = xts_Elec['2010-02-17']
lxts_Elec.fit = list(); lts_Elec.fit = list()
lxts_Elec.prev = list(); lts_Elec.prev = list()
time.Elec.prev = list()
for (i in 1:4){
  # Create a list of xts object.
  lxts_Elec.fit[[i]] = xts_Elec.fit[.indexmin(xts_Elec.fit) == 15*(i-1)]
  lxts_Elec.prev[[i]] = xts_Elec.prev[.indexmin(xts_Elec.prev) == 15*(i-1)]
  # Create list of time series object
  if (i == 1)
  lts_Elec.fit[[i]] = ts(coredata(lxts_Elec.fit[[i]]), frequency = 24, start = c(1,3))
else
lts_Elec.fit[[i]] = ts(coredata(lxts_Elec.fit[[i]]), frequency = 24, start = c(1,2))
lts_Elec.prev[[i]] = ts(coredata(lxts_Elec.prev[[i]]), frequency = 24, start = c(48,1))
# Prepare time of each forecasted data part
time.Elec.prev[[i]] = time(lxts_Elec.prev[[i]])
}
```

### Forecast using all data and check the residuals
```{r "2.10.b. Forecast using all data and check the residuals"}
fit.all = list(); prev.all = list(); lxts_prev.all = list()
# Forecast and convert the results to xts objects.
for (i in 1:4){
  # SARIMA(0,1,7)(0,1,1)[24]
  fit.all[[i]] = Arima(lts_Elec.fit[[i]][, 'Power'], order = c(0,1,7), seasonal = c(0,1,1))
  prev.all[[i]] = forecast(fit.all[[i]], h = 24)
  lxts_prev.all[[i]] = xts(prev.all[[i]]$mean, order.by = time.Elec.prev[[i]])
  # Check residuals of SARIMA(0,1,7)(0,1,1)[24]
  cat ('* --- Data', i, '(Minute', 15*(i-1), 'of each hour) --- *\n')
  checkresiduals(fit.all[[i]])
}
# Concatenate the 4 parts of forecasted data
xts_prev.all = do.call(rbind, lxts_prev.all)
```
* --- Data 1 (Minute 0 of each hour) --- *

	Ljung-Box test

data:  Residuals from ARIMA(0,1,7)(0,1,1)[24]
Q* = 55.541, df = 40, p-value = 0.05205

Model df: 8.   Total lags used: 48

* --- Data 2 (Minute 15 of each hour) --- *

	Ljung-Box test

data:  Residuals from ARIMA(0,1,7)(0,1,1)[24]
Q* = 47.397, df = 40, p-value = 0.1964

Model df: 8.   Total lags used: 48

* --- Data 3 (Minute 30 of each hour) --- *

	Ljung-Box test

data:  Residuals from ARIMA(0,1,7)(0,1,1)[24]
Q* = 49.548, df = 40, p-value = 0.1432

Model df: 8.   Total lags used: 48

* --- Data 4 (Minute 45 of each hour) --- *

	Ljung-Box test

data:  Residuals from ARIMA(0,1,7)(0,1,1)[24]
Q* = 45.816, df = 40, p-value = 0.2435

Model df: 8.   Total lags used: 48

### Plot the forecasted time series
```{r "2.10.c. Plot the forecasted time series"}
xts_prevAndTest = cbind(xts_prev.all, xts_Elec.fit['2010-02-10/2010-02-16', 'Power'])
names(xts_prevAndTest) = c("Forecast data", "True data")
autoplot(xts_prevAndTest, facets = NULL) +
  labs(x = 'Days', y = 'Power (kW)') +
  ggtitle("Forecast from SARIMA(0,1,7)(0,1,1)[24] method with last week of data") +
  theme(legend.position="bottom")
```

### Save forecasted data
```{r "2.10.d Save forecasted data"}
write.xlsx(xts_prev.all, "MohamedAbid.xlsx", startCol = 1, startRow = 1, colNames = F)
```

#---------------------------------------------------------------------------------------------#
# III. Forecast using outdoor temperature

## 1. Prepare data
```{r "3.1. Prepare data"}
lts_Elec.test = list()
for (i in 1:4){
  lts_Elec.test[[i]] = ts(coredata(lxts_Elec.test[[i]]), frequency = 24, start = c(47,1))
}
```

## 2. Time series regression models
```{r "3.2.a. fit"}
fit4.tslm = list()
for (i in 1:4){
  cat ('* --- Data', i, '(Minute', 15*(i-1), 'of each hour) --- *\n')
  fit4.tslm[[i]] = tslm(Power ~ Temp, data = lts_Elec.train[[i]])
  print(summary(fit4.tslm[[i]])$coefficients)
}
```
* --- Data 1 (Minute 0 of each hour) --- *
             Estimate Std. Error  t value     Pr(>|t|)
(Intercept) 121.90648  6.2528623 19.49611 6.044955e-73
Temp         10.13939  0.5619213 18.04414 5.878409e-64
* --- Data 2 (Minute 15 of each hour) --- *
              Estimate Std. Error t value     Pr(>|t|)
(Intercept) 125.906242  6.2258309 20.2232 1.393582e-77
Temp          9.836683  0.5594398 17.5831 3.466375e-61
* --- Data 3 (Minute 30 of each hour) --- *
             Estimate Std. Error  t value     Pr(>|t|)
(Intercept) 122.12009  6.2151792 19.64868 6.427208e-74
Temp         10.16157  0.5584826 18.19495 7.007388e-65
* --- Data 4 (Minute 45 of each hour) --- *
             Estimate Std. Error t value     Pr(>|t|)
(Intercept) 120.27623  6.3047106 19.0772 2.525370e-70
Temp         10.25806  0.5665277 18.1069 2.406676e-64

```{r "3.2.b Check residuals"}
for (i in 1:4){
# Check residuals
cat ('* --- Data', i, '(Minute', 15*(i-1), 'of each hour) --- *\n')
checkresiduals(fit4.tslm[[i]], test = 'LB', plot = F)
}
```

## 3. SARIMA
```{r "3.3.a fit"}
fit4.resd = list()
for (i in 1:4){
  titleOfPlot = paste('Residuals of Data ', i, ' (Minute ', 15*(i-1), ' of each hour)' , sep='')
  fit4.resd[[i]] = fit4.tslm[[i]]$residuals
  ggtsdisplay(fit4.resd[[i]], main = titleOfPlot)
}
```

### Differencing the residuals : lag=24
```{r "3.3.b. Differencing the residuals : lag=24"}
resd.diff0 = list()
for (i in 1:4){
  titleOfPlot = paste('diff(lag=24) Residuals of data ', i, ' (Minute ', 15*(i-1), ' of each hour)' ,
                      sep='')
  resd.diff0[[i]] = diff(fit4.resd[[i]], lag = 24)
  ggtsdisplay(resd.diff0[[i]], main = titleOfPlot)
}
```

### Differencing the residuals : lag(lag=24)
```{r "3.3.c. Differencing the residuals : lag(lag=24)"}
resd.diff1 = list()
for (i in 1:4){
  titleOfPlot = paste('diff(diff(lag=24)) Residuals of data ', i, ' (Minute ', 15*(i-1),
                      ' of each hour)' , sep='')
  resd.diff1[[i]] = diff(resd.diff0[[i]])
  ggtsdisplay(resd.diff1[[i]], main = titleOfPlot)
}
```

### SARIMA(0,1,3)(0,1,1)[24] for the residuals
```{r "3.3.d. SARIMA(0,1,3)(0,1,1)24 for the residuals"}
fit4.arima1.resd = list()
for (i in 1:4){
  # Fit with SARIMA(0,1,3)(0,1,1)[24] on the residuals
  fit4.arima1.resd[[i]] = Arima(fit4.resd[[i]], order = c(0,1,3), seasonal = c(0,1,1))
  # Check residuals
  cat ('* --- Data', i, '(Minute', 15*(i-1), 'of each hour) --- *\n')
  checkresiduals(fit4.arima1.resd[[i]])
}
```
* --- Data 1 (Minute 0 of each hour) --- *

	Ljung-Box test

data:  Residuals from ARIMA(0,1,3)(0,1,1)[24]
Q* = 85.642, df = 44, p-value = 0.0001722

Model df: 4.   Total lags used: 48

* --- Data 2 (Minute 15 of each hour) --- *

	Ljung-Box test

data:  Residuals from ARIMA(0,1,3)(0,1,1)[24]
Q* = 76.213, df = 44, p-value = 0.001846

Model df: 4.   Total lags used: 48

* --- Data 3 (Minute 30 of each hour) --- *

	Ljung-Box test

data:  Residuals from ARIMA(0,1,3)(0,1,1)[24]
Q* = 77.2, df = 44, p-value = 0.001458

Model df: 4.   Total lags used: 48

* --- Data 4 (Minute 45 of each hour) --- *

	Ljung-Box test

data:  Residuals from ARIMA(0,1,3)(0,1,1)[24]
Q* = 82.82, df = 44, p-value = 0.0003595

Model df: 4.   Total lags used: 48

### SARIMA(0,1,7)(0,1,1)[24] for the residuals
```{r "3.3.e. SARIMA(0,1,7)(0,1,1)24 for the residuals"}
fit4.arima2.resd = list()
for (i in 1:4){
  # Fit with SARIMA(0,1,7)(0,1,1)[24] on the residuals
  fit4.arima2.resd[[i]] = Arima(fit4.resd[[i]], order = c(0,1,7), seasonal = c(0,1,1))
  # Check residuals
  cat ('* --- Data', i, '(Minute', 15*(i-1), 'of each hour) --- *\n')
  checkresiduals(fit4.arima2.resd[[i]], plot = F)
}
```
* --- Data 1 (Minute 0 of each hour) --- *

	Ljung-Box test

data:  Residuals from ARIMA(0,1,7)(0,1,1)[24]
Q* = 45.695, df = 40, p-value = 0.2474

Model df: 8.   Total lags used: 48

* --- Data 2 (Minute 15 of each hour) --- *

	Ljung-Box test

data:  Residuals from ARIMA(0,1,7)(0,1,1)[24]
Q* = 42.985, df = 40, p-value = 0.3446

Model df: 8.   Total lags used: 48

* --- Data 3 (Minute 30 of each hour) --- *

	Ljung-Box test

data:  Residuals from ARIMA(0,1,7)(0,1,1)[24]
Q* = 32.239, df = 40, p-value = 0.8038

Model df: 8.   Total lags used: 48

* --- Data 4 (Minute 45 of each hour) --- *

	Ljung-Box test

data:  Residuals from ARIMA(0,1,7)(0,1,1)[24]
Q* = 38.736, df = 40, p-value = 0.5271

Model df: 8.   Total lags used: 48

### SARIMA(0,1,7)(0,1,1)[24] for data with covariates
```{r "3.3.f. SARIMA(0,1,7)(0,1,1)24 for data with covariates"}
fit4.arima11.cov = list(); prev4.arima11.cov = list(); lxts_prev4.arima11.cov = list()
fit4.arima12.cov = list(); prev4.arima12.cov = list(); lxts_prev4.arima12.cov = list()
# Forecast and convert the results to xts objects.
for (i in 1:4){
  # SARIMA(0,1,7)(0,1,1)[24]
  fit4.arima11.cov[[i]] = Arima(lts_Elec.train[[i]][, 'Power'], order = c(0,1,7),
                                seasonal = c(0,1,1), xreg = lts_Elec.train[[i]][, 'Temp'])
  prev4.arima11.cov[[i]] = forecast(fit4.arima11.cov[[i]], xreg = lts_Elec.test[[i]][, 'Temp'],
                                    h = 24)
  lxts_prev4.arima11.cov[[i]] = xts(prev4.arima11.cov[[i]]$mean, order.by = time.Elec.test[[i]])
  # SARIMA(0,1,7)(0,1,1)[24] + Box-Cox
  fit4.arima12.cov[[i]] = Arima(lts_Elec.train[[i]][, 'Power'], lambda = 'auto', order = c(0,1,7),
                                seasonal = c(0,1,1), xreg = lts_Elec.train[[i]][, 'Temp'])
  prev4.arima12.cov[[i]] = forecast(fit4.arima12.cov[[i]], xreg = lts_Elec.test[[i]][, 'Temp'],
                                    h = 24)
  lxts_prev4.arima12.cov[[i]] = xts(prev4.arima12.cov[[i]]$mean, order.by = time.Elec.test[[i]])
}
# Concatenate the 4 parts of forecasted data
xts_prev4.arima11.cov = do.call(rbind, lxts_prev4.arima11.cov)
xts_prev4.arima12.cov = do.call(rbind, lxts_prev4.arima12.cov)
# Compute the RMSE
rmse4.arima11.cov = RMSE.val(xts_prev4.arima11.cov, xts_Elec.test[, 'Power'])
rmse4.arima12.cov = RMSE.val(xts_prev4.arima12.cov, xts_Elec.test[, 'Power'])
# Print the RMSE
cat ('RMSE of SARIMA(0,1,7)(0,1,1)[24] using covariates =', rmse4.arima11.cov, '\n')
cat ('RMSE of SARIMA(0,1,7)(0,1,1)[24] with Box-Cox using covariates =', rmse4.arima12.cov, '\n')
```
- RMSE of SARIMA(0,1,7)(0,1,1)[24] using covariates = 14.5565 
---
- RMSE of SARIMA(0,1,7)(0,1,1)[24] with Box-Cox using covariates = 14.55678 
---

```{r 3.3.g. Check residuals}
for (i in 1:4){
  # Check residuals
  cat ('* --- Data', i, '(Minute', 15*(i-1), 'of each hour) --- *\n')
  checkresiduals(fit4.arima11.cov[[i]], plot = F)
}
```

## 4. Auto ARIMA with Covariates
```{r "3.4. Auto ARIMA with Covariates"}
fit4.autoArima1.cov = list(); prev4.autoArima1.cov = list(); lxts_prev4.autoArima1.cov = list()
fit4.autoArima2.cov = list(); prev4.autoArima2.cov = list(); lxts_prev4.autoArima2.cov = list()
# Forecast and convert the results to xts objects.
for (i in 1:4){
  # SARIMA(0,1,7)(0,1,1)[24]
  fit4.autoArima1.cov[[i]] = auto.arima(lts_Elec.train[[i]][, 'Power'],
  xreg = lts_Elec.train[[i]][, 'Temp'])
  prev4.autoArima1.cov[[i]] = forecast(fit4.autoArima1.cov[[i]],
  xreg = lts_Elec.test[[i]][, 'Temp'], h = 24)
  lxts_prev4.autoArima1.cov[[i]] = xts(prev4.autoArima1.cov[[i]]$mean,
  order.by = time.Elec.test[[i]])
  # SARIMA(0,1,7)(0,1,1)[24] + Box-Cox
  fit4.autoArima2.cov[[i]] = auto.arima(lts_Elec.train[[i]][, 'Power'], lambda = 'auto',
  xreg = lts_Elec.train[[i]][, 'Temp'])
  prev4.autoArima2.cov[[i]] = forecast(fit4.autoArima2.cov[[i]],
  xreg = lts_Elec.test[[i]][, 'Temp'], h = 24)
  lxts_prev4.autoArima2.cov[[i]] = xts(prev4.autoArima2.cov[[i]]$mean,
  order.by = time.Elec.test[[i]])
}
# Concatenate the 4 parts of forecasted data
xts_prev4.autoArima1.cov = do.call(rbind, lxts_prev4.autoArima1.cov)
xts_prev4.autoArima2.cov = do.call(rbind, lxts_prev4.autoArima2.cov)
# Compute the RMSE
rmse4.autoArima1.cov = RMSE.val(xts_prev4.autoArima1.cov, xts_Elec.test[, 'Power'])
rmse4.autoArima2.cov = RMSE.val(xts_prev4.autoArima2.cov, xts_Elec.test[, 'Power'])
# Print the RMSE
cat ('RMSE of Auto ARIMA using covariates =', rmse4.autoArima1.cov, '\n')
cat ('RMSE of Auto ARIMA with Box-Cox using covariates =', rmse4.autoArima2.cov, '\n')
```
- RMSE of Auto ARIMA using covariates = 17.85662 
---
- RMSE of Auto ARIMA with Box-Cox using covariates = 16.12468
---

## 5. NNET with Covariates
```{r "3.5. NNET with Covariates"}
fit4.nnet1.cov = list(); prev4.nnet1.cov = list(); lxts_prev4.nnet1.cov = list()
fit4.nnet2.cov = list(); prev4.nnet2.cov = list(); lxts_prev4.nnet2.cov = list()
# Forecast and convert the results to xts objects.
for (i in 1:4){
# SARIMA(0,1,7)(0,1,1)[24]
fit4.nnet1.cov[[i]] = nnetar(lts_Elec.train[[i]][, 'Power'],
xreg = lts_Elec.train[[i]][, 'Temp'])
prev4.nnet1.cov[[i]] = forecast(fit4.nnet1.cov[[i]],
xreg = lts_Elec.test[[i]][, 'Temp'], h = 24)
lxts_prev4.nnet1.cov[[i]] = xts(prev4.nnet1.cov[[i]]$mean,
order.by = time.Elec.test[[i]])
# SARIMA(0,1,7)(0,1,1)[24] + Box-Cox
fit4.nnet2.cov[[i]] = nnetar(lts_Elec.train[[i]][, 'Power'], lambda = 'auto',
xreg = lts_Elec.train[[i]][, 'Temp'])
prev4.nnet2.cov[[i]] = forecast(fit4.nnet2.cov[[i]],
xreg = lts_Elec.test[[i]][, 'Temp'], h = 24)
lxts_prev4.nnet2.cov[[i]] = xts(prev4.nnet2.cov[[i]]$mean,
order.by = time.Elec.test[[i]])
}
# Concatenate the 4 parts of forecasted data
xts_prev4.nnet1.cov = do.call(rbind, lxts_prev4.nnet1.cov)
xts_prev4.nnet2.cov = do.call(rbind, lxts_prev4.nnet2.cov)
# Compute the RMSE
rmse4.nnet1.cov = RMSE.val(xts_prev4.nnet1.cov, xts_Elec.test[, 'Power'])
rmse4.nnet2.cov = RMSE.val(xts_prev4.nnet2.cov, xts_Elec.test[, 'Power'])
# Print the RMSE
cat ('RMSE of NNET using covariates =', rmse4.nnet1.cov, '\n')
cat ('RMSE of NNET with Box-Cox using covariates =', rmse4.nnet2.cov, '\n')
```
- RMSE of NNET using covariates = 16.03902 
---
- RMSE of NNET with Box-Cox using covariates = 16.372 
---

## 6. Vectoriel Auto-Regressive models

### Select the best VARp model
```{r "3.6.a. Select the best VARp model"}
for (i in 1:4){
  cat ('* --- Data', i, '(Minute', 15*(i-1), 'of each hour) --- *\n')
  print(VARselect(lts_Elec.train[[i]], lag.max = 7, type = "both", season = 24))
}
```
* --- Data 1 (Minute 0 of each hour) --- *
$selection
AIC(n)  HQ(n)  SC(n) FPE(n) 
     2      2      1      2 

$criteria
               1         2         3         4         5         6         7
AIC(n)  4.501248  4.488496  4.489289  4.493797  4.498039  4.503271  4.507242
HQ(n)   4.594522  4.588679  4.596382  4.607798  4.618950  4.631092  4.641971
SC(n)   4.747749  4.753257  4.772310  4.795077  4.817579  4.841070  4.863300
FPE(n) 90.131313 88.989708 89.060815 89.463716 89.844733 90.316731 90.676870

* --- Data 2 (Minute 15 of each hour) --- *
$selection
AIC(n)  HQ(n)  SC(n) FPE(n) 
     1      1      1      1 

$criteria
               1         2         3         4         5         6         7
AIC(n)  4.245767  4.249480  4.247368  4.249425  4.254292  4.260599  4.257696
HQ(n)   4.338969  4.349586  4.354377  4.363338  4.375110  4.388320  4.392322
SC(n)   4.492089  4.514048  4.530182  4.550485  4.573598  4.598151  4.613495
FPE(n) 69.810667 70.070708 69.923230 70.067647 70.410032 70.856019 70.651301

* --- Data 3 (Minute 30 of each hour) --- *
$selection
AIC(n)  HQ(n)  SC(n) FPE(n) 
     1      1      1      1 

$criteria
               1         2         3         4         5         6         7
AIC(n)  4.272868  4.275453  4.278853  4.283470  4.287274  4.293254  4.291419
HQ(n)   4.366070  4.375559  4.385862  4.397383  4.408091  4.420975  4.426044
SC(n)   4.519190  4.540021  4.561667  4.584530  4.606580  4.630806  4.647217
FPE(n) 71.728494 71.914517 72.159787 72.494162 72.770963 73.208045 73.074456

* --- Data 4 (Minute 45 of each hour) --- *
$selection
AIC(n)  HQ(n)  SC(n) FPE(n) 
     3      2      1      3 

$criteria
               1         2         3         4         5         6         7
AIC(n)  4.499497  4.486951  4.486066  4.489825  4.494335  4.500443  4.500018
HQ(n)   4.592699  4.587056  4.593076  4.603739  4.615152  4.628164  4.634643
SC(n)   4.745819  4.751519  4.768880  4.790886  4.813641  4.837995  4.855816
FPE(n) 89.973639 88.852291 88.774249 89.109133 89.512484 90.061636 90.024180

### Estimate and check residuals of a VAR2 model
```{r "3.6.b. Estimate and check residuals of a VAR2 model"}
var = list()
for (i in 1:4){
  # Estimation of a VAR2
  var[[i]] = VAR(lts_Elec.train[[i]], p = 2, type = "both", season = 24, exogen = NULL)
  # Check residuals
  cat ('* --- Data', i, '(Minute', 15*(i-1), 'of each hour) --- *\n')
  print(serial.test(var[[i]], lags.pt = 10, type = "PT.asymptotic"))
}
```
* --- Data 1 (Minute 0 of each hour) --- *

	Portmanteau Test (asymptotic)

data:  Residuals of VAR object var[[i]]
Chi-squared = 36.623, df = 32, p-value = 0.2628

* --- Data 2 (Minute 15 of each hour) --- *

	Portmanteau Test (asymptotic)

data:  Residuals of VAR object var[[i]]
Chi-squared = 44.525, df = 32, p-value = 0.06954

* --- Data 3 (Minute 30 of each hour) --- *

	Portmanteau Test (asymptotic)

data:  Residuals of VAR object var[[i]]
Chi-squared = 44.158, df = 32, p-value = 0.07462

* --- Data 4 (Minute 45 of each hour) --- *

	Portmanteau Test (asymptotic)

data:  Residuals of VAR object var[[i]]
Chi-squared = 35.578, df = 32, p-value = 0.3035

### Forecast usin the VAR2 model
```{r "3.6.c. Forecast usin the VAR2 model"}
prev4.var = list(); lxts_prev4.var = list()
# Forecast and convert the results to xts objects.
for (i in 1:4){
  prev4.var[[i]] = forecast(var[[i]], h = 24)
  lxts_prev4.var[[i]] = xts(prev4.var[[i]]$forecast$Power$mean, order.by = time.Elec.test[[i]])
}
# Concatenate the 4 parts of forecasted data
xts_prev4.var = do.call(rbind, lxts_prev4.var)
# Compute the RMSE
rmse4.var = RMSE.val(xts_prev4.var, xts_Elec.test[, 'Power'])
# Print the RMSE
cat ('RMSE of VAR =', rmse4.var, '\n')
```
- RMSE of VAR = 16.85849
---

## 7. Choose the model

### Model summary
```{r "3.7.a. Model summary"}
df = data.frame(RMSE = c(rmse4.arima11.cov, rmse4.autoArima2.cov, rmse4.nnet1.cov, rmse4.var))
rownames(df) = c("SARIMA(0,1,7)(0,1,1)[24] using temperature", 
                 "Auto ARIMA + Box-Cox using temperature", "NNET using temperature",
                 "Vectoriel Auto-Regressive models")
print(df)
```
	                                              RMSE
                                               <dbl>
SARIMA(0,1,7)(0,1,1)[24] using temperature	14.55650			
Auto ARIMA + Box-Cox using temperature	    16.12468			
NNET using temperature	                    16.03902			
Vectoriel Auto-Regressive models          	16.85849	

### Plot
```{r 3.7.b. Plot}
xts_prevAndTest = cbind(xts_prev4.arima11.cov, xts_Elec.test[, 'Power'])
names(xts_prevAndTest) = c("SARIMA(0,1,7)(0,1,1)[24] using outdoor temperature", "True data")
autoplot(xts_prevAndTest, facets = NULL) + labs(x = 'Days', y = 'Power (kW)') +
  theme(legend.position="bottom")
```

## 8. Forecast using all data

### Forecast
```{r "3.8.a. Forecast"}
fit.cov.all = list(); prev.cov.all = list(); lxts_prev.cov.all = list()
# Forecast and convert the results to xts objects.
for (i in 1:4){
  # SARIMA(0,1,7)(0,1,1)[24] using covariates
  fit.cov.all[[i]] = Arima(lts_Elec.fit[[i]][, 'Power'], xreg = lts_Elec.fit[[i]][, 'Temp'],
                           order = c(0,1,7), seasonal = c(0,1,1))
  prev.cov.all[[i]] = forecast(fit.cov.all[[i]], xreg = lts_Elec.prev[[i]][, 'Temp'], h = 24)
  lxts_prev.cov.all[[i]] = xts(prev.cov.all[[i]]$mean, order.by = time.Elec.prev[[i]])
}
# Concatenate the 4 parts of forecasted data
xts_prev.cov.all = do.call(rbind, lxts_prev.cov.all)
```

### Check residuals for the selected model
```{r "3.8.b. Check residuals for the selected model"}
for (i in 1:4){
  cat ('* --- Data', i, '(Minute', 15*(i-1), 'of each hour) --- *\n')
  checkresiduals(fit.cov.all[[i]], plot = F)
}
```

* --- Data 1 (Minute 0 of each hour) --- *

	Ljung-Box test

data:  Residuals from Regression with ARIMA(0,1,7)(0,1,1)[24] errors
Q* = 53.888, df = 39, p-value = 0.05676

Model df: 9.   Total lags used: 48

* --- Data 2 (Minute 15 of each hour) --- *

	Ljung-Box test

data:  Residuals from Regression with ARIMA(0,1,7)(0,1,1)[24] errors
Q* = 48.54, df = 39, p-value = 0.1407

Model df: 9.   Total lags used: 48

* --- Data 3 (Minute 30 of each hour) --- *

	Ljung-Box test

data:  Residuals from Regression with ARIMA(0,1,7)(0,1,1)[24] errors
Q* = 49.336, df = 39, p-value = 0.1242

Model df: 9.   Total lags used: 48

* --- Data 4 (Minute 45 of each hour) --- *

	Ljung-Box test

data:  Residuals from Regression with ARIMA(0,1,7)(0,1,1)[24] errors
Q* = 44.96, df = 39, p-value = 0.2364

Model df: 9.   Total lags used: 48

### Plot the forecasted data
```{r "3.8.c. Plot the forecasted data"}
xts_prevAndTest = cbind(xts_prev.cov.all, xts_Elec.fit['2010-02-10/2010-02-16', 'Power'])
names(xts_prevAndTest) = c("Forecast data using outdoor temperature", "True data")
autoplot(xts_prevAndTest, facets = NULL) +
  labs(x = 'Days', y = 'Power (kW)') +
  ggtitle("Forecast from SARIMA(0,1,7)(0,1,1)[24] method with last week of data") +
  theme(legend.position="bottom")
```

### Save forecasted data with covariates
```{r "3.8.d. Save forecasted data with covariates"}
wb = loadWorkbook('MohamedAbid.xlsx')
writeData(wb, 1, xts_prev.cov.all, startCol = 2, startRow = 1, colNames = F)
saveWorkbook(wb, 'MohamedAbid.xlsx', overwrite = T)
```







